Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-06-14 paper/results.tex
implement more Nikos comments

\subsubsection{Hyperparameter Tuning}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{exp1_slice0}
	\includegraphics[width=0.9\linewidth]{exp1_slice1}
	\includegraphics[width=0.9\linewidth]{exp1_slice2}
	\caption{\label{fig:exp1-time-vs-reg}20~best-performing surrogates per each considered family, plotted in
		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) with 3~selected discrete feature assignments.}
\end{figure}

@@

\subsubsection{Scaling Benchmark}

@@

\subsubsection{Model Comparison}
In Experiment~4, we aim to create models that yield:
(a)~the best regression performance regardless
of other features, (b)~acceptable performance with the shortest mean
prediction time, or (c)~acceptable performance with the smallest training set.
To this end, we trained 8~surrogates that are presented in~\Fref{fig:reg-performance}
and~\Tref{tbl:exp4-detailed-results}.
Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
Experiments~2 \&~3, we utilised the best-performing hyperparameters.
In pursuit of goal~(a), the best approximator (Model~1,
ANN) achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
to a standard deviation of error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
with respect to the MC TBR evaluation baseline. Satisfying
goal~(b), the fastest model (Model~2, ANN) achieved~$R^2=\num{0.985}$,
$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
and~$\omega=\num{8659251} \times$.
While these surrogates
were trained on the entire available set of~\num{500000} datapoints, to satisfy
goal~(c) we also trained a more simplified model (Model~4, GBT)
that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with a set of size only~\num{10000}.

@@

\begin{figure}
	\centering
	\hspace*{-1.5em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.pdf}
	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
\end{figure}

\begin{figure}
	\centering
	\hspace*{-1.5em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and baseline scheme, with 100k initial samples.}
\end{figure}

>>>>

\subsubsection{Hyperparameter Tuning}
\label{sec:res-exp12}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{exp1_slice0}
	\includegraphics[width=0.9\linewidth]{exp1_slice1}
	\includegraphics[width=0.9\linewidth]{exp1_slice2}
	\caption{\label{fig:exp1-time-vs-reg}Results of Experiment~1, 20~best-performing surrogates per each considered family, plotted in
		terms of computational complexity (as~$\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) with 3~selected discrete feature assignments out
		of~4.}
\end{figure}

@@

\subsubsection{Scaling Benchmark}
\label{sec:res-exp3}

@@

\subsubsection{Model Comparison}
\label{sec:res-exp4}

In Experiment~4, we aim to create models that yield:
(a)~the best regression performance regardless
of other features, (b)~acceptable performance with the shortest mean
prediction time, or (c)~acceptable performance with the smallest training set.
To this end, we trained 8~surrogates that are presented in~\Fref{fig:reg-performance}
and~\Tref{tbl:exp4-detailed-results}.
Having selected ANNs, GBTs, ERTs, RBFs and SVMs based on the results of
Experiments~2 \&~3, we utilised the best-performing hyperparameters.
In pursuit of goal~(a), the best approximator (Model~1,
ANN) achieved~$R^2=\num{0.998}$ and mean prediction
time~$\overline{t}_{\text{pred.}}=\SI{1.124}{\micro\second}$. These correspond
to a standard deviation of error~$S=\num{0.013}$ and a relative speedup~$\omega=\num{6916416} \times$
with respect to the MC TBR evaluation baseline. Satisfying
goal~(b), the fastest model (Model~2, ANN) achieved~$R^2=\num{0.985}$,
$\overline{t}_{\text{pred.}}=\SI{0.898}{\micro\second}$, $S=\num{0.033}$
and~$\omega=\num{8659251} \times$.
While these surrogates
were trained on the entire available set of~\num{500000} datapoints, to satisfy
goal~(c) we also trained a more simplified model (Model~4, GBT)
that achieved~$R^2=\num{0.913}$,
$\overline{t}_{\text{pred.}}=\SI{6.125}{\micro\second}$, $S=\num{0.072}$ and $\omega=\num{1269777} \times$
with a set of size only~\num{10000}.

@@

\begin{figure}
	\centering
	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig7_qasssampling.pdf}
	\caption{\label{fig:qasssampling}Absolute training error for QASS, baseline scheme, and mixed scheme.}
\end{figure}

\begin{figure}
	\centering
	\hspace*{-1.4em}\includegraphics[width=1.15\linewidth]{fig8_qasssampling100k.pdf}
	\caption{\label{fig:qasssampling100k}Absolute training error for QASS and baseline scheme, with 100k initial samples.}
\end{figure}
